Hospital classification in Scotland

### 2022-02-21 hospital_classification.Rmd
Added a little bit to hospital classifications following AG's comments about hospitals without A&E units

```{r}
write_csv(hospital_classification, file = "./hospital_classification/hospital_classification.csv")
```

>>>>

```{r}
write_csv(hospital_classification, file = "./hospital_classification/hospital_classification.csv")

## acute hospitals only
write_csv(
  hospital_classification %>% filter(acute), 
  file = "./hospital_classification/hospital_classification_acute_only.csv")
```

# Further considerations

## Hospitals without A&E units

On 24 January 2022, Andrew Gasiorowski contacted me to check if we should include hospitals the following hospitals which no longer have A&E units and only MIU (minor injuries units). We could remove these from the 'acute hospitals' list since they don't :

* Golden Jubilee
* New Stobhill 
* New Victoria

All of the above hospitals are classed as `Other - Miscellaneous hospitals in which function and/or costs are not comparable with other hospitals`.

MIU is likely not the place a person might have gone to seek help for COVID-related symptoms, however, it's possible that some hospitalisations staretd with a MIU visit, e.g. for falls

This may not be a big issue if the MIUs are close to A&Es, in which case the A&Es are a good approximation in terms of location.

```{r}
hospital_classification %>% 
  filter(acute) %>%
  filter(str_detect(org_loc, regex("stobhill|new victoria|jubilee", ignore_case = TRUE)))
```

# Session info

```{r}
sessionInfo()
```
